---
title: "Tensorflow_testing"
author: "Michael Huang"
date: "2023-03-25"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# set the path to your Python executable
install.packages("reticulate")
library(reticulate)
use_python("/Users/michaelhuang/Library/r-miniconda-arm64/envs/r-reticulate/bin/python")

```

```{r}
# set the path to your TensorFlow conda environment
use_condaenv("/Users/michaelhuang/Library/r-miniconda-arm64/envs/r-reticulate")
```

```{r message=FALSE, warning=FALSE}
tensorflow <- import("tensorflow")
library(tensorflow)
install_tensorflow( version = "latest", upgrade = TRUE)
```

```{r}
library(keras)
library(tfdatasets)
```

Let’s download and extract the dataset, then explore the directory structure.

```{r}
url <- "https://ai.stanford.edu/~amaas/data/sentiment/aclImdb_v1.tar.gz"

dataset <- get_file(
  "aclImdb_v1",
  url,
  untar = TRUE,
  cache_dir = '.',
  cache_subdir = ''
)

dataset_dir <- file.path("aclImdb")
```

```{r}
list.files(dataset_dir)
```

```{r}
train_dir <- file.path(dataset_dir, 'train')
list.files(train_dir)
```

The aclImdb/train/pos and aclImdb/train/neg directories contain many text files, each of which is a single movie review. Let’s take a look at one of them.

```{r}
sample_file <- file.path(train_dir, 'pos/1181_9.txt')
readr::read_file(sample_file)
```

Next, you will load the data off disk and prepare it into a format suitable for training. To do so, you will use the helpful text_dataset_from_directory utility, which expects a directory structure as follows.

main_directory/
...class_a/
......a_text_1.txt
......a_text_2.txt
...class_b/
......b_text_1.txt
......b_text_2.txt
To prepare a dataset for binary classification, you will need two folders on disk, corresponding to class_a and class_b. These will be the positive and negative movie reviews, which can be found in aclImdb/train/pos and aclImdb/train/neg. As the IMDB dataset contains additional folders, you will remove them before using this utility.

```{r}
remove_dir <- file.path(train_dir, 'unsup')
unlink(remove_dir, recursive = TRUE)
```

Next, you will use the text_dataset_from_directory utility to create a labeled TensorFlow Dataset. tfdatasets is a powerful collection of tools for working with data.

When running a machine learning experiment, it is a best practice to divide your dataset into three splits: train, validation, and test.

The IMDB dataset has already been divided into train and test, but it lacks a validation set. Let’s create a validation set using an 80:20 split of the training data by using the validation_split argument below.
```{r}
batch_size <- 32
seed <- 42

raw_train_ds <- text_dataset_from_directory(
  'aclImdb/train',
  batch_size = batch_size,
  validation_split = 0.2,
  subset = 'training',
  seed = seed
)
```

As you can see above, there are 25,000 examples in the training folder, of which you will use 80% (or 20,000) for training. As you will see in a moment, you can train a model by passing a dataset directly to fit(). If you’re new to tfdatasets, you can also iterate over the dataset and print out a few examples as follows.
```{r}
library(coro)
batch <- raw_train_ds %>%
  reticulate::as_iterator() %>%
  coro::collect(n = 1)

batch[[1]][[1]][1]
```
```{r}
batch[[1]][[2]][1]
```

Notice the reviews contain raw text (with punctuation and occasional HTML tags like <br/>). You will show how to handle these in the following section.

The labels are 0 or 1. To see which of these correspond to positive and negative movie reviews, you can check the class_names property on the dataset.

```{r}
cat("Label 0 corresponds to", raw_train_ds$class_names[1])
```

```{r}
cat("Label 1 corresponds to", raw_train_ds$class_names[2])
```

Next, you will create a validation and test dataset. You will use the remaining 5,000 reviews from the training set for validation.

Note: When using the validation_split and subset arguments, make sure to either specify a random seed, or to pass shuffle = FALSE, so that the validation and training splits have no overlap.

```{r}
raw_val_ds <- text_dataset_from_directory(
  'aclImdb/train',
  batch_size = batch_size,
  validation_split = 0.2,
  subset = 'validation',
  seed = seed
)
```

```{r}
raw_test_ds <- text_dataset_from_directory(
  'aclImdb/test',
  batch_size = batch_size
)
```

Next, you will standardize, tokenize, and vectorize the data using the helpful layer_text_vectorization() layer.

Standardization refers to preprocessing the text, typically to remove punctuation or HTML elements to simplify the dataset. Tokenization refers to splitting strings into tokens (for example, splitting a sentence into individual words, by splitting on whitespace). Vectorization refers to converting tokens into numbers so they can be fed into a neural network. All of these tasks can be accomplished with this layer.

As you saw above, the reviews contain various HTML tags like <br />. These tags will not be removed by the default standardizer in the TextVectorization layer (which converts text to lowercase and strips punctuation by default, but doesn’t strip HTML). You will write a custom standardization function to remove the HTML.

Note: To prevent training-testing skew (also known as training-serving skew), it is important to preprocess the data identically at train and test time. To facilitate this, the text_vectorization layer can be included directly inside your model, as shown later in this tutorial.

```{r}
# creating a regex with all punctuation characters for replacing.
re <- reticulate::import("re")

punctuation <- c("!", "\\", "\"", "#", "$", "%", "&", "'", "(", ")", "*",
"+", ",", "-", ".", "/", ":", ";", "<", "=", ">", "?", "@", "[",
"\\", "\\", "]", "^", "_", "`", "{", "|", "}", "~")

punctuation_group <- punctuation %>%
  sapply(re$escape) %>%
  paste0(collapse = "") %>%
  sprintf("[%s]", .)

custom_standardization <- function(input_data) {
  lowercase <- tf$strings$lower(input_data)
  stripped_html <- tf$strings$regex_replace(lowercase, '<br />', ' ')
  tf$strings$regex_replace(
    stripped_html,
    punctuation_group,
    ""
  )
}
```

Next, you will create a TextVectorization layer. You will use this layer to standardize, tokenize, and vectorize our data. You set the output_mode to int to create unique integer indices for each token.

Note that you’re using the default split function, and the custom standardization function you defined above. You’ll also define some constants for the model, like an explicit maximum sequence_length, which will cause the layer to pad or truncate sequences to exactly sequence_length values.

```{r}
max_features <- 10000
sequence_length <- 250

vectorize_layer <- layer_text_vectorization(
  standardize = custom_standardization,
  max_tokens = max_features,
  output_mode = "int",
  output_sequence_length = sequence_length
)
```

Next, you will call adapt() to fit the state of the preprocessing layer to the dataset. This will cause the model to build an index of strings to integers.

Note: It’s important to only use your training data when calling adapt (using the test set would leak information).

```{r}
# Make a text-only dataset (without labels), then call adapt
train_text <- raw_train_ds %>%
  dataset_map(function(text, label) text)
vectorize_layer %>% adapt(train_text)
```

Let’s create a function to see the result of using this layer to preprocess some data.

```{r}
vectorize_text <- function(text, label) {
  text <- tf$expand_dims(text, -1L)
  list(vectorize_layer(text), label)
}
```

```{r}
# retrieve a batch (of 32 reviews and labels) from the dataset
batch <- reticulate::as_iterator(raw_train_ds) %>%
  reticulate::iter_next()
first_review <- as.array(batch[[1]][1])
first_label <- as.array(batch[[2]][1])
cat("Review:\n", first_review)
```
```{r}
cat("Label: ", raw_train_ds$class_names[first_label+1])
```

Vectorized review: 
```{r}
print(vectorize_text(first_review, first_label))
```
As you can see above, each token has been replaced by an integer. You can lookup the token (string) that each integer corresponds to by calling .get_vocabulary() on the layer.
```{r}
cat("9257 ---> ",get_vocabulary(vectorize_layer)[9257 + 1]) # because R is onde indexed
```

```{r}
cat(" 15 ---> ",get_vocabulary(vectorize_layer)[15 + 1])
```

```{r}
cat("Vocabulary size: " , length(get_vocabulary(vectorize_layer)))
```

You are nearly ready to train your model. As a final preprocessing step, you will apply the text_vectorization layer you created earlier to the train, validation, and test dataset.
```{r}
train_ds <- raw_train_ds %>% dataset_map(vectorize_text)
val_ds <- raw_val_ds %>% dataset_map(vectorize_text)
test_ds <- raw_test_ds %>% dataset_map(vectorize_text)
```

These are two important methods you should use when loading data to make sure that I/O does not become blocking.

dataset_cache() keeps data in memory after it’s loaded off disk. This will ensure the dataset does not become a bottleneck while training your model. If your dataset is too large to fit into memory, you can also use this method to create a performant on-disk cache, which is more efficient to read than many small files.

dataset_prefetch() overlaps data preprocessing and model execution while training.

You can learn more about both methods, as well as how to cache data to disk in the data performance guide.

```{r}
AUTOTUNE <- tf$data$AUTOTUNE

train_ds <- train_ds %>%
  dataset_cache() %>%
  dataset_prefetch(buffer_size = AUTOTUNE)
val_ds <- val_ds %>%
  dataset_cache() %>%
  dataset_prefetch(buffer_size = AUTOTUNE)
test_ds <- test_ds %>%
  dataset_cache() %>%
  dataset_prefetch(buffer_size = AUTOTUNE)
```

It’s time to create your neural network:
```{r}
embedding_dim <- 16
```

```{r}
model <- keras_model_sequential() %>%
  layer_embedding(max_features + 1, embedding_dim) %>%
  layer_dropout(0.2) %>%
  layer_global_average_pooling_1d() %>%
  layer_dropout(0.2) %>%
  layer_dense(1)

summary(model)
```
The layers are stacked sequentially to build the classifier:

The first layer is an embedding layer. This layer takes the integer-encoded reviews and looks up an embedding vector for each word-index. These vectors are learned as the model trains. The vectors add a dimension to the output array. The resulting dimensions are: (batch, sequence, embedding). To learn more about embeddings, check out the Word embeddings tutorial.
Next, a global_average_pooling_1d layer returns a fixed-length output vector for each example by averaging over the sequence dimension. This allows the model to handle input of variable length, in the simplest way possible.
This fixed-length output vector is piped through a fully-connected (dense) layer with 16 hidden units.
The last layer is densely connected with a single output node.

Loss function and optimizer
A model needs a loss function and an optimizer for training. Since this is a binary classification problem and the model outputs a probability (a single-unit layer with a sigmoid activation), you’ll use losses$BinaryCrossentropy loss function.

Now, configure the model to use an optimizer and a loss function:
```{r}
model %>% compile(
  loss = loss_binary_crossentropy(from_logits = TRUE),
  optimizer = 'adam',
  metrics = metric_binary_accuracy(threshold = 0)
)
```

Train the model
You will train the model by passing the dataset object to the fit method.

```{r}
epochs <- 10
history <- model %>% 
  fit(
    train_ds,
    validation_data = val_ds,
    epochs = epochs
  )
```

```{r}
model %>% evaluate(test_ds)
```
In the code above, you applied the text_vectorization layer to the dataset before feeding text to the model. If you want to make your model capable of processing raw strings (for example, to simplify deploying it), you can include the text_vectorization layer inside your model. To do so, you can create a new model using the weights you just trained.
```{r}
export_model <- keras_model_sequential() %>%
  vectorize_layer() %>%
  model() %>%
  layer_activation(activation = "sigmoid")

export_model %>% compile(
  loss = loss_binary_crossentropy(from_logits = FALSE),
  optimizer = "adam",
  metrics = 'accuracy'
)

# Test it with `raw_test_ds`, which yields raw strings
export_model %>% evaluate(raw_test_ds)
```
```{r}
examples <- c(
  "The movie was great!",
  "The movie was okay.",
  "The movie was terrible..."
)

predict(export_model, examples)
```

